---
title: "My RMarkdown"
author: "My Name"
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[CO, CE]{My Name}
- \usepackage{float}
output:
  html_document:
    df_print: paged
geometry: left=1in,right=1.2in,top=1in,bottom=1in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(nlme)
library(car)
library(MASS)
library(knitr)
library(ggplot2)
```


Used to control the output printing.
```{r, echo=FALSE}
## adapted from the post: https://community.rstudio.com/t/showing-only-the-first-few-lines-of-the-results-of-a-code-chunk/6963
library(knitr)
hook_output <- knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  lines <- options$output.lines
  if (is.null(lines)) {
    return(hook_output(x, options))  # pass to default hook
  }
  x <- unlist(strsplit(x, "\n"))
  more <- "..."
  if (length(lines)==1) {        # first n lines
    if (length(x) > lines) {
      # truncate the output, but add ....
      x <- c(head(x, lines), more)
    }
  } else {
    x <- c(more, x[lines], more)
  }
  # paste these lines together
  x <- paste(c(x, ""), collapse = "\n")
  hook_output(x, options)
})
```

### (i) Sections

Suppress warnings.
```{r warning=FALSE}

```

Don't evaluate code blocks.
```{r eval=FALSE}

```

Hide code blocks.
```{r echo=FALSE}

```

Hide results.
```{r results='hide'}

```

Hide figures.
```{r fig.show='hide'}

```


Print only part of the output result. To find the number of lines, try using a text editor such as Sublime.
```{r output.lines = c(6:10, 20:32)}

```

Set figure captions and labels.
```{r echo = FALSE, fig.cap="Contour plots, upper row shows contour plots for Design = 1, lower row for Design=2.\\label{fig:contour}"}

```

Set figure height and similar properties. 
```{r fig.height=4}

```

Conclusion of methods.


Sample text:

*Considerations for model building*: `block` and `Machine` should be included in the model. Use 
**cv.glmnet{glmnet}** to choose penalty parameter.

*Residual Diagnostics*: Residual plots are as shown in Figure \ref{fig:residual}.



\newpage

## Appendices
### Appendix A: Figures
```{r, echo = FALSE, fig.width = 4, fig.cap="residual plots\\label{fig:residual}"}
#include_graphics('image-path')
```

### Appendix B: Tables
