---
title: "STAT 8051 Week 2 Lab"
author: "Yu Yang"
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[CO, CE]{}
- \usepackage{float}
output:
  pdf_document: default
  html_document:
    df_print: paged
geometry: left=1in,right=1.2in,top=1in,bottom=1in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(alr4)
```

```{r, echo=FALSE}
## adapted from the post: https://community.rstudio.com/t/showing-only-the-first-few-lines-of-the-results-of-a-code-chunk/6963
library(knitr)
hook_output <- knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  lines <- options$output.lines
  if (is.null(lines)) {
    return(hook_output(x, options))  # pass to default hook
  }
  x <- unlist(strsplit(x, "\n"))
  more <- "..."
  if (length(lines)==1) {        # first n lines
    if (length(x) > lines) {
      # truncate the output, but add ....
      x <- c(head(x, lines), more)
    }
  } else {
    x <- c(more, x[lines], more)
  }
  # paste these lines together
  x <- paste(c(x, ""), collapse = "\n")
  hook_output(x, options)
})
```

# Linear Model Basic Analysis

Use the **fuel2001** dataset in **alr4** as an example.

```{r}
library(alr4)
data("fuel2001")
dat <- data.frame(Tax = fuel2001$Tax, Dlic = fuel2001$Drivers/fuel2001$Pop*1000, 
                  Income = fuel2001$Income/1000, 
                  logMiles = log(fuel2001$Miles),
                  Fuel = fuel2001$FuelC/fuel2001$Pop*1000)
# View(dat)
summary(dat)
```

Fit a linear model using all variables.

```{r output.lines = 9:21}
m0 <- lm(Fuel ~ ., data = dat)
summary(m0)
```

## Interpretation of coefficients

(1) Fitted equation

$Fuel = 154.1928 + -4.2280*Tax + 0.4719*Dlic + -6.1353*Income + 26.7552*logMiles$

(2) Significance of variables

Check the corresponding p-values.

## Estimate of the covariance matrix of $\beta$

Estimate of $\sigma$
```{r}
(sigma.hat <- summary(m0)$sigma)
```

Estimate of $Cov(\beta) = \sigma^2(X^TX)^{-1}$
```{r}
vcov(m0)
```

Estimate of $(X^TX)^{-1}$.
```{r}
summary(m0)$cov.unscaled  # directly using the summary output
vcov(m0)/(sigma.hat^2)  # using the covariance matrix
```

## Hypothesis testing and confidence interval

### Case 1: consider only one coefficient, $\beta_i$

#### Two-sided test

$H_0: \beta_1 = 0 \quad vs. \quad H_1: \beta_1 \neq 0$

T-test: use the p-value in `summary(m0)`. 

F-test: 
```{r output.lines = 3:7}
m1 <- update(m0, ~ .-Tax, data = dat)
anova(m0, m1)
```

#### One-sided test

$H_0: \beta_1 = 0 \quad vs. \quad H_1: \beta_1 < 0$

T-test: use the p-value in `summary(m0)`, p-value = 0.042873 / 2 = 0.0214365.

$H_0: \beta_1 = 0 \quad vs. \quad H_1: \beta_1 > 0$

T-test: use the p-value in `summary(m0)`, p-value =  1- 0.042873 / 2 = 0.9785635.

#### Confidence interval

Use the `Estimate` and `Std.Error` in `summary(m0)`. Or use `confint()`.
```{r}
beta1.hat <- summary(m0)$coefficients[2, 1]
beta1.se <- summary(m0)$coefficients[2, 2]

df <- 51-5  # n-p
#uses t quantiles
c(beta1.hat-qt(0.975, df)*beta1.se, beta1.hat+qt(0.975, df)*beta1.se)
confint(m0)[2, ]

# uses normal quantiles
c(beta1.hat-qnorm(0.975)*beta1.se, beta1.hat+qnorm(0.975)*beta1.se)
confint.default(m0)[2, ]
```

### Case 2: consider the linear combination of the coefficients, $a^T\beta$

$H_0: \beta_1 = \beta_2 + \beta_3 \quad vs. \quad H_1: \beta_1 > \beta_2 + \beta_3$

Note $a^T\hat{\beta} \sim N(a^T\beta, a^T\sigma^2(X^TX)^{-1}a)$ and 
$\frac{a^T\hat{\beta}}{se(a^T\hat{\beta})} \sim_{H_0} t_{n-p}$.
```{r}
a <- c(0, 1, -1, -1, 0)
(estimate <- t(a)%*%summary(m0)$coefficient[, 1])
(se <- t(a)%*%vcov(m0)%*%a)
(t.value <- estimate / se)
(p.value <- pt(t.value, df, lower.tail = FALSE))  # cannot reject H0

# confidence interval
c(estimate - qt(0.975, df)*se, estimate + qt(0.975, df)*se)
```

